Project proposal: Explanations for unexplained effect size heterogeneity

### 2023-06-14 supplement/supplement_A.qmd
changed supplement names to match manuscript appearance order

---
format: pdf
---

@@

# Supplement A: varying reliability SD and the effect of N and k

```{r Figure A1, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_A_fig1.png")
```

```{r Figure A2, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_A_fig2.png")
```

```{r Figure A3, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_A_fig3.png")
```

>>>>

---

format: pdf

---
# Supplement A: converting heterogeneity between Pearson's r and Fisher's z

@@

The table below shows the results of our procedure to convert between studies variance expressed in Pearson's $r$ to between-studies variance expressed in Fisher's $z$ through the use of $I^2$ as described in the main text.

_Table A1_.
```{r}

source("../code/01_compute_tau_fishers_z.r") #all computations were made here

#Gives us the object 'cond'
cond_table <- cond[,c(1, 3, 2, 4, 6)]

knitr::kable(cond_table, booktabs = TRUE, col.names = c("$\\rho$", "N", "$\\tau_r$", "$I^2$", "$\\tau_z$"), escape = FALSE)
```

_Note._ $\rho$ = average effect size, N = (fixed) within-study sample size, $\tau_r$ = between-studies standard deviation in Pearson's $r$, $\tau_z$ between-studies standard deviation in Fisher's $z$. The $I^2$ statistic is here expressed as a proportion.

### 2023-06-14 supplement/supplement_B.qmd
changed supplement names to match manuscript appearance order

```{r Figure 1, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_B_fig1.png")
```

_Figure 1._ Bias in heterogeneity estimates in the absence of unreliability in primary studies (i.e., reliability = 1). The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to truncation in Pearson's $r$ or translation to Fisher's $z$ these values may differ from actual true heterogeneity standard deviation (black solid lines).

@@

```{r Figure 2, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_B_fig2.png")
```

_Figure 2._ Removal of the dependency between effect size and sampling variance removes the positive bias in heterogeneity estimates for larger true heterogeneity when using Pearson's $r$. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations averaged across 1e3 repetitions. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to truncation in Pearson's $r$ or translation to Fisher's $z$ these values may differ from actual true heterogeneity standard deviation (black solid lines).

>>>>

```{r Figure B1, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_B_fig1.png")
```

_Figure B1._ Bias in heterogeneity estimates in the absence of unreliability in primary studies (i.e., reliability = 1). The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to truncation in Pearson's $r$ or translation to Fisher's $z$ these values may differ from actual true heterogeneity standard deviation (black solid lines).

@@

```{r Figure B2, echo=FALSE, out.width = '100%'}
knitr::include_graphics("../figures/supplement/supplement_B_fig2.png")
```

_Figure B2._ Removal of the dependency between effect size and sampling variance removes the positive bias in heterogeneity estimates for larger true heterogeneity when using Pearson's $r$. The x-axis indicates average effect size and the y-axis estimated heterogeneity in standard deviations averaged across 1e3 repetitions. Columns indicate the nominal true heterogeneity standard deviation $\tau$. Due to truncation in Pearson's $r$ or translation to Fisher's $z$ these values may differ from actual true heterogeneity standard deviation (black solid lines).
